Quality Definitions of Qualities

### 2019-10-09 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
convert to LIPIcs format

\documentclass[12pt]{article}

@@

\begin{document}

\title{Quality Definitions of Qualities} 
\author{Spencer Smith, Jacques Carette, Olu Owojaiye,\\Peter Michalski and Ao Dong}
\date{\today}

\maketitle

@@

\bibliographystyle {plainnat}
\bibliography {../../CommonFiles/ResearchProposal}

>>>>

\documentclass[letterpaper,cleveref]{lipics-v2019}

@@

\title{Quality Definitions of Qualities} 
\author{Spencer Smith}{McMaster University, Canada}{smiths@mcmaster.ca}{}{}
\author{Jacques Carette}{McMaster University, Canada}{carette@mcmaster.ca}{}{}
\author{Olu Owojaiye}{McMaster University, Canada}{}{}{}
\author{Peter Michalski}{McMaster University, Canada}{}{}{}
\author{Ao Dong}{McMaster University, Canada}{}{}{}

\authorrunning{Smith et al.}
\Copyright{Spencer Smith and Jacques Carette and Olu Owojaiye and Peter Michalski and Ao Dong}

\date{\today}

\hideLIPIcs
\nolinenumbers

\begin{document}
\maketitle

@@

\bibliographystyle {plainurl}
\bibliography {../../CommonFiles/ResearchProposal}
